Endogenous Politics and \\ the Design of Trade Institutions

### 2017-01-04 to-do.tex
remove superfluous notes and combine others in to-do

\section{``Dynamic preferences''}
	\begin{itemize}
					\item Gul and Pesendorfer's (2001) Econometrica is a two-period model. No dynamic inconsistency; derive temptation and desire for commitment in a model with dynamically consistent preferences.
					\item Even better, especially advertising example (credit Kyle): Becker, Gary. S. and George J. Stigler, ``De Gustibus Non Est Disputandum,'' The American Economic Review, Vol. 67, No. 2 (Mar., 1977), pp. 76-90
					\item Simpler: Becker, G. S. and K. M. Murphy (1993), Simple Theory of Advertising as a Good or Bad, Quarterly Journal of Economics, 942-64.
						\begin{itemize}
							\item Their firms are my firm. Their consumers are my government
							\item Kyle's lit review talkes about `persuasive,' `informative,' and `complementary' views of advertisting. This is complementary.
							\item $e$ and $\tau$ enter objective function. Gov't is sophisticated, can make commitment that alters $e$ (i.e. behavior of another actor). But $CS + \ga(e)PS + \ldots$, just like $u(X,Y,A)$; says consumer could work to pass law about number of adds on TV each hour.
							\item Use newly drawn extensive form to explain this, lays out when welfare is realized
							\item Addresses James' concern about needing to be more precise about when $\ga$ is evaluated)
			\begin{itemize}
				\item Skeptical of comparative-static style result: can I really compare governments with different $\ga$'s?
			\end{itemize}

				\end{itemize}
			\item Mostafa, Nuno, Giovanni, Anson to some extent: Cardinal vs. ordinal
				\begin{itemize}
					\item Giovanni: if I can show properties survive  monotonic transformation, I'm fine
					\item They don't like gov't choosing its own preferences. May just need to change wording
				\end{itemize}
			\item Bob: what is fundamental structure of preferences?
			\item The way $e$ affects preferences doesn't change!!! Preferences are wrapped up in $\ga$!
				\begin{itemize}
					\item ``How the assumption of a non-unitary legislature translates into this incentive constraint. In the non-unitary legislature, if the current period incentive constraint includes any future value of lobbying effort, this would mean the current-period median legislator evaluating her current-period incentive constraint using a mixture of her own political-economy weight with those of the legislators who are median in the future in the trade agreement and trade-war scenarios. The first major step I have taken to clarify the incentive constraint is the analysis in Appendix B.1 of the unitary model. I discuss the differences between the unitary and non-unitary models in the beginning of that Appendix.''
					\item ``Note that the median legislator, whose identity is determined by the lobby's effort level $e_b$, evaluates future payoffs according to her own political economy weight, $\ga(e_b)$. Of course, depending on legislator $e_b$'s choice, either legislator $e_a$ or legislator $e_{tw}$ will be the decision maker in those future periods. But legislator $e_b$, who is the decision maker in the current period, maximizes her own welfare given the predicted behavior of future decision makers.''

				\end{itemize}
			\item Devashish: Utility fcn didn't change. Just got evaluated at a different point
				\begin{itemize}
					\item Preferences don't change. It's persuasion that affects decision-making. 2nd story: Giovanni's ``expost $\ga(e)$ as effort to elect/choose ex-post decision-maker''
				\end{itemize}
		\end{itemize}

\section{Lobbying cost included in gov't welfare}
	\begin{itemize}
		\item Kyle: why doesn't government (dis)value expenditure by lobby? Needs to be counted in government welfare function or justify why not
			\begin{itemize}
				\item Rohan: $(1-a)\cdot C + a \cdot W \equiv C + a \cdot (W-C)$
				\item When weights on $\pi_X$ are not linear, what are the implications for resource waste? Is it the same as $+ C / - C$?
			\end{itemize}
		\item Subtracting $e$ gives me the kind of non-monotonicity I'd like in the graphs.
			\begin{itemize}
				\item Does it do anything to the analysis? Just shifts govt's ideal point
			\end{itemize}
		\item JIE$\_$revision: I have also verified that \emph{none} of the results of the model change if lobbying effort is subtracted from the legislative/executive welfare function (except, of course, the evaluated level of welfare). I have refrained from adding the ``$-e$'' to the welfare function out of a desire to be consistent with the existing literature.
		\item I think I'd like to just change to the ``$-e$'' version.
			\begin{itemize}
				\item Worries: won't match literature. Want to make analogies to GH, DGH, MRC, LT.
			\end{itemize}
	\end{itemize}

@@

				\item I've supplied the suggested results to connect my model to that of Dixit, Grossman and Helpman (1997) in Appendix B.2, along with some text pointing to it at the end of Section 2.2 on page 10. The results from the DGH-style model are qualitatively different in a minor way. I discuss this difference in Appendix B.1 where I present a unitary government/legislature version of the model that most closely matches Maggi and Rodriguez-Clare 2007.
				\item The model does admit an interpretation in which the same branch of government both negotiates the trade agreement and decides on the applied tariff ex-post. In this sense, the structure of the one-shot game shares much in common with Maggi and Rodriguez-Clare 2007.
				\item The fact that the applied tariffs are equal to the negotiated binding is reminiscent of Maggi and Rodriguez-Clare 2007. Exactly the same dynamic is at play here: specifying trade agreement tariffs as caps instead of strong bindings keeps the lobby active during periods where the trade agreement is honored. In Appendix B.3, I analyze the model with strong bindings and show that the results would be altered in magnitude but not in spirit by assuming that the trade agreement tariffs are strong bindings instead of tariff caps. The only change to the model is that under strong bindings there would be zero lobbying effort during a trade agreement phase as the lobby would not need to exert effort to bid protection levels up to the trade agreement tariff. There would still be no disputes in equilibrium, but the lobbying constraint is easier to satisfy with strong bindings because the gap between trade war and trade agreement profits shrinks when the lobby stops exerting effort to receive the trade agreement tariff. Because lower trade agreement tariffs can be sustained under strong bindings, executive and legislators with small political economy weights prefer a strong-binding agreement and legislators with high political economy weights prefer a weak-binding agreement.

@@

				\item The model admits this `one-branch' interpretation only if the one branch is non-unitary
				\item the model analyzed in the body of this paper can be given an interpretation in line with Maggi and Rodriguez-Clare 2007 if capital is completely mobile in the long run and the single decision-making body is non-unitary. In Appendix B.1, I compare the results of this paper to those from a model with a unitary government, as this would seem to bring the model most closely into alignment with Maggi and Rodriguez-Clare 2007 and a large part of the literature. Then, in Appendix B.2, since the government welfare function used in this paper can be interpreted as a special case of the one proposed by DGH97, I will show that a model patterned after DGH97 and specialized to this environment---which is also a unitary model---provides results that are qualitatively similar to the unitary model.
				\item I have added Appendix B.1 with analysis of the unitary model
						\item In the model with a non-unitary government, the lobby's effort $e$ determines the identity of the decision maker. Thus the decision maker at the time the lobby is pushing for the agreement to be broken ($e=e_b>e_a$ in order to have a median legislator who will break the agreement) is different from the decision maker during the trade war phase $(e = e_{tw})$ and the decision maker during a trade agreement phase ($e=e_a(\tau^a)$). The weight on the lobbying industry's profits changes with lobbying effort because lobbying effort determines a different median voter in the legislature or government more generally. However, when the median voter during a `break' phase is evaluating her incentive constraint, she values future tariff choices --- which will be determined by whoever is median in the future --- with her own preferences. Although she will not be the decision maker in the future, there is no reason for her to evaluate future welfare according to some other legislator's preference.
						\item If the model is interpreted as having a unitary government, there is only one decision maker. There is a fixed mapping from lobbying effort to the weight the decision maker places on the lobby's profits, and the realization of this weight changes with the realization of lobbying effort. Thus, predicting future lobbying effort, the decision maker knows what the realization of her weight on the lobby's profits will be and evaluates the incentive constraint accordingly. Expression (10) would be modified while the lobbying constraint is unchanged.
				\item Appendix B.2 with analysis of DGH model
						\item I claim that the government welfare function presented in this paper can be interpreted as a special case of the general welfare function proposed in DGH97. They specify government welfare as $G(a,c)$ where $a$ is the policy vector $\left(\left(\tau,\tau^*\right)\right)$ and $c$ is a vector of payments from each lobby ($e$).
						\item Here I examine a version of the DGH97 model specialized to this environment. Because the DGH97 model is fundamentally a unitary government model, the relevant benchmark is the unitary version of the model. The results of the two unitary models are qualitatively the same.

@@

						\item In the auction-menu set-up of the DGH97 model, there does not seem to be a natural alternative to the unitary government interpretation. The lobby offers a contribution schedule of effort levels and tariffs and the government chooses among these pairs. In the non-unitary model, each different effort level determines a different government, so the government cannot choose between elements of a schedule. To analyze this model, I make the standard assumptions of a unitary government and that the lobby has all the bargaining power.
						\item Denote the government's welfare function as $W_G(\tau,\tau^*,e(\tau)) = W(\tau,\tau^*) + g(e(\tau))$ where $W = CS_X + PS_X + CS_Y + PS_Y +TR$ is social welfare. Then do analysis...
				\item Appendix B.3 with analysis of the strong binding case. 
						\item If the trade agreement involves strong bindings instead of tariff caps (i.e. weak bindings), the legislature must deliver $\tau^a$ and the lobby's optimal effort during a period in which the trade agreement holds is $e_a = 0$. That the lobby pays less---here, nothing---for the protection it receives under the trade agreement is the only change from the base model. This means that nothing changes in the trade war. Likewise the legislature's repeated-game incentive constraint is unchanged. But the lobby's incentive constraint IS changed...
						\item As in MRC, tariff caps in this model serve to keep the lobby `in the game.' A tariff cap makes the lobby's self-enforcement constraint harder to satisfy and thus requires a higher trade agreement tariff for self-enforcement. From the ex-ante point of view, strong bindings are therefore preferable. Tariff caps could be viewed as a way to commit to setting higher trade agreement tariffs and therefore as a mechanism for ensuring that rents are distributed to protectionists ex-post.
		\item Comparison to GH94
				\item Contingent payments are hard to reconcile with uncertainty
				\item It's the truthful contribution schedule in GH94 that implies the constant weighting of $1+a$ for sectors represented by a lobby. Won't get this clean, constant weighting with other schedules.
				\item Gov't doesn't care about \textit{anything} because it gets the same payoff no matter what
						\item With one lobby, this lobby-has-all-the-bargaining-power feature is an equilibrium implication of the menu-auction set-up where the lobby makes a TIOLI offer
						\item Gov't gets all the surplus when there are two or more lobbies
						\item This result holds in DGH97, p. 767. Footnote 10 explicitly says that this is because lobby makes TIOLI offer.
						\item So go to MRC07 where bargaining power can be manipulated
				\item Menu auction eqm requirement: $(C(\tau),\tau)$ must maximize joint surplus
						\item NB: $\tau$ that maximizes gov't welfare doesn't generically maximize joint surplus (unless it also maximizes lobby payoff)
						\item In my model, optimum for lobby would be prohibitive tariff, $e=0$. Joint optimum determined by $\frac{\partial \ga}{\partial e}\pi_X = 2$ and $\frac{\partial CS_X}{\partial \tau} + \left[ 1 + \ga(e)\right]\frac{\partial \pi_X}{\partial \tau} + \frac{\partial TR}{\partial \tau} = 0$. Not clear how this is related to lobby's problem, but likely to have higher $\tau$ and lower $e$ than government's optimum (unless $\ga$ changes very steeply between the two points $e_J$ and $e_G$)
						\item Careful of transferable vs. non-transferable utility
				\item Not sure if contingent vs. non-contingent payments are a big deal
				\item If I change nothing else but subtract $C$ from gov't welfare function, no qualitative change b/c of 0 bargaining weight
		\item MRC07
				\item Need case of fixed capital ($z=0$)
				\item NB (p. 1391): optimal trade agreement if lobbies have all the bargaining power and no ex-ante lobbying is free trade
						\item Page 26-28 of working paper has government with all the bargaining power (and no capital mobility, but remember that the capital owners choose where to invest in the first period). Here, could be free trade but could be interior to get some rents.
				\item Then re-do MRC07 with $W(\tau) + g(e)$, and version where I subtract $e$
						\item Should have gov't make lobby indifferent and maximize joint surplus. But again, this doesn't necessarily maximize gov't welfare
						\item Or rather, should I follow Limao and Tovar?

@@

\section{Lit review}
\begin{itemize}
	\item Find MRC cites (maybe some in Ethier) for why PE shocks can't be addressed
		\begin{itemize}
			\item Bagwell and Staiger 1999 AER
		\end{itemize}
	\item Have to make connection to endogenous papers clearer
		\begin{itemize}
			\item and make clear that GH is isomorphic / provides microfoundations for Baldwin objective function
			\item More on Coates $\&$ Ludema (2001)
		\end{itemize}
	\item I think that I need to bring people along more carefully from GH/MRC to what I'm doing
	\item Paola: How do I want to sell the paper?
		\begin{itemize}
			\item In relation to what literature?
				\begin{itemize}
					\item What literature does endogenous? Coates-Ludema 2001, MRC, GH
					\item What literature \textit{doesn't}?
				\end{itemize}
			\end{itemize}
	\item Review Bown, Bagwell $\&$ Staiger
	\item Do I include papers like BS2001 (non-repeated) in lit review?
	\item Read Rosendorff $\&$ Milner (2001) [from Cristiane Carneiro at PEIO]
	\item Kyle: McLaren in his chapter calls the Grossman and Helpman setup with
	 contributions 'felonious'
	\item David DeRemer: Safeguards have dropped off in use around the world
		\begin{itemize}
			\item Look at U.S. vs. ROW (he sent papers)
		\end{itemize}
	\item Limao and Tovar 2011
		\begin{enumerate}
			\item Their 2nd (and final) stage is Nash bargaining. Is there an isomorphism to my setup?
			\item It IS clear to take their first, limited case of commitment to tariff cap only (ignore NTB) as analogy for gov't in my model choosing commitment to different tariff level. Need to answer Q1 above in order to answer points 3 and 4:
			\item Their gains from commitment derive from improvement in bargaining power vis-a-vis the lobby (Schelling conjecture invoked). How does this relate to the gain from commitment in my model?
			\item Top of page 6: ``large enough bargaining power.'' Can I make connection to $\ga(e)$?
			\item Note: in their equation 3, $C$ enters expression for NBS's ($\tau$) in equilibrium, it doesn't disappear as in GH
		\end{enumerate}
\end{itemize}

@@

\section{Motivation}
		\begin{itemize}
			\item What it's missing: intersection with reality
				\begin{itemize}
					\item Anecdotes
					\item How policy is used
						\begin{itemize}
							\item I thought that escape clause implications \textit{were} this
						\end{itemize}
					\item Something like how GH predicts export taxes but it doesn't work that way in the real world
					\item Well articulated question / paradox
				\end{itemize}
			\item Look at ``Theory of Managed Trade'' model motivation (BS)
			\item Intro doesn't reflect body of paper
			\item What kinds of empirical questions might we ask with this model?
			\item What would be different because we use this model?
			\item Starting from the introduction, I think you make a convincing case that it is important to endogenize the extent of political pressure and I believe this would be THE selling point of the paper. However, you have not completely sold your contribution and its novelty that you bring in the issue of the objective function of the government. Is this aspect crucial for the point you want to make? If yes, it should be integrate with the previous object from the beginning. If not, it should be postponed a bit.
			\item I also find the introduction too long. You could/should split the literature review that begins on page 4 to a separate section. And in any case, I found that you don't engage with the literature in terms of how you contribute/differentiate from it. Again, your main point seems to get lost into the discussion instead of standing out.
			\item You need to think a bit more about the objective(s) of the paper and how best to achieve them.
			\item Intro: GH gives micro foundations. But there are real consequences of endogenous politics
		\end{itemize}

>>>>

\section{``Dynamic preferences''}
	\begin{itemize}
		\item Becker, G. S. and K. M. Murphy (1993), Simple Theory of Advertising as a Good or Bad, Quarterly Journal of Economics, 942-64.
			\begin{itemize}
				\item Their firms are my firm. Their consumers are my government
				\item Kyle's lit review talkes about `persuasive,' `informative,' and `complementary' views of advertisting. This is complementary.
				\item $e$ and $\tau$ enter objective function. Gov't is sophisticated, can make commitment that alters $e$ (i.e. behavior of another actor). But $CS + \ga(e)PS + \ldots$, just like $u(X,Y,A)$; says consumer could work to pass law about number of ads on TV each hour.
				\item Use newly drawn extensive form to explain this, lays out when welfare is realized
				\item Addresses James' concern about needing to be more precise about when $\ga$ is evaluated
					\begin{itemize}
						\item Skeptical of comparative-static style result: can I really compare governments with different $\ga$'s?
					\end{itemize}
			\end{itemize}
		\item Mostafa, Nuno, Giovanni, Anson to some extent: Cardinal vs. ordinal
				\begin{itemize}
					\item Giovanni: if I can show properties survive  monotonic transformation, I'm fine
					\item They don't like gov't choosing its own preferences. May just need to change wording
				\end{itemize}
		\item Bob: what is fundamental structure of preferences?
		\item The way $e$ affects preferences doesn't change!!! Preferences are wrapped up in $\ga$!
			\begin{itemize}
				\item ``How the assumption of a non-unitary legislature translates into this incentive constraint. In the non-unitary legislature, if the current period incentive constraint includes any future value of lobbying effort, this would mean the current-period median legislator evaluating her current-period incentive constraint using a mixture of her own political-economy weight with those of the legislators who are median in the future in the trade agreement and trade-war scenarios. The first major step I have taken to clarify the incentive constraint is the analysis in Appendix B.1 of the unitary model. I discuss the differences between the unitary and non-unitary models in the beginning of that Appendix.''
				\item ``Note that the median legislator, whose identity is determined by the lobby's effort level $e_b$, evaluates future payoffs according to her own political economy weight, $\ga(e_b)$. Of course, depending on legislator $e_b$'s choice, either legislator $e_a$ or legislator $e_{tw}$ will be the decision maker in those future periods. But legislator $e_b$, who is the decision maker in the current period, maximizes her own welfare given the predicted behavior of future decision makers.''
			\end{itemize}
		\item Devashish: Utility fcn didn't change. Just got evaluated at a different point
				\begin{itemize}
					\item Preferences don't change. It's persuasion that affects decision-making. 2nd story: Giovanni's ``expost $\ga(e)$ as effort to elect/choose ex-post decision-maker''
				\end{itemize}
		\end{itemize}

\section{Lobbying cost included in gov't welfare}
	\begin{itemize}
		\item Kyle: why doesn't government (dis)value expenditure by lobby? Needs to be counted in government welfare function or justify why not
			\begin{itemize}
				\item Rohan: $(1-a)\cdot C + a \cdot W \equiv C + a \cdot (W-C)$
				\item When weights on $\pi_X$ are not linear, what are the implications for resource waste? Is it the same as $+ C / - C$?
			\end{itemize}
		\item Subtracting $e$ gives me the kind of non-monotonicity I'd like in the graphs.
			\begin{itemize}
				\item Does it do anything to the analysis? Just shifts govt's ideal point
			\end{itemize}
		\item I think I'd like to just change to the ``$-e$'' version.
			\begin{itemize}
				\item Worries: won't match literature. Want to make analogies to GH, DGH, MRC, LT.
			\end{itemize}
	\end{itemize}

@@

				\item The model does admit an interpretation in which the same branch of government both negotiates the trade agreement and decides on the applied tariff ex-post, as long as the one branch is non-unitary. The model analyzed in the body of this paper can be given an interpretation in line with Maggi and Rodriguez-Clare 2007 if capital is completely mobile in the long run. In Appendix B.1, I compare the results of this paper to those from a model with a unitary government, as this would seem to bring the model most closely into alignment with Maggi and Rodriguez-Clare 2007 and a large part of the literature.

@@

				\item The fact that the applied tariffs are equal to the negotiated binding is reminiscent of Maggi and Rodriguez-Clare 2007. Exactly the same dynamic is at play here: specifying trade agreement tariffs as caps instead of strong bindings keeps the lobby active during periods where the trade agreement is honored. In Appendix B.3, I analyze the model with strong bindings and show that the results would be altered in magnitude but not in spirit by assuming that the trade agreement tariffs are strong bindings instead of tariff caps. The only change to the model is that under strong bindings there would be zero lobbying effort during a trade agreement phase as the lobby would not need to exert effort to bid protection levels up to the trade agreement tariff. There would still be no disputes in equilibrium, but the lobbying constraint is easier to satisfy with strong bindings because the gap between trade war and trade agreement profits shrinks when the lobby stops exerting effort to receive the trade agreement tariff. Because lower trade agreement tariffs can be sustained under strong bindings, executive and legislators with small political economy weights prefer a strong-binding agreement and legislators with high political economy weights prefer a weak-binding agreement. A tariff cap makes the lobby's self-enforcement constraint harder to satisfy and thus requires a higher trade agreement tariff for self-enforcement. From the ex-ante point of view, strong bindings are therefore preferable. Tariff caps could be viewed as a way to commit to setting higher trade agreement tariffs and therefore as a mechanism for ensuring that rents are distributed to protectionists ex-post.

				\item I have added Appendix B.1 with analysis of the unitary model
					\begin{itemize}
						\item In the model with a non-unitary government, the lobby's effort $e$ determines the identity of the decision maker. Thus the decision maker at the time the lobby is pushing for the agreement to be broken ($e=e_b>e_a$ in order to have a median legislator who will break the agreement) is different from the decision maker during the trade war phase $(e = e_{tw})$ and the decision maker during a trade agreement phase ($e=e_a(\tau^a)$). The weight on the lobbying industry's profits changes with lobbying effort because lobbying effort determines a different median voter in the legislature or government more generally. However, when the median voter during a `break' phase is evaluating her incentive constraint, she values future tariff choices --- which will be determined by whoever is median in the future --- with her own preferences. Although she will not be the decision maker in the future, there is no reason for her to evaluate future welfare according to some other legislator's preference.
						\item If the model is interpreted as having a unitary government, there is only one decision maker. There is a fixed mapping from lobbying effort to the weight the decision maker places on the lobby's profits, and the realization of this weight changes with the realization of lobbying effort. Thus, predicting future lobbying effort, the decision maker knows what the realization of her weight on the lobby's profits will be and evaluates the incentive constraint accordingly. Expression (10) would be modified while the lobbying constraint is unchanged.
					\end{itemize}
				\item Appendix B.2 with analysis of DGH model
					\begin{itemize}
						\item I claim that the government welfare function presented in this paper can be interpreted as a special case of the general welfare function proposed in DGH97. They specify government welfare as $G(a,c)$ where $a$ is the policy vector $\left(\left(\tau,\tau^*\right)\right)$ and $c$ is a vector of payments from each lobby ($e$).

@@

						\item Denote the government's welfare function as $W_G(\tau,\tau^*,e(\tau)) = W(\tau,\tau^*) + g(e(\tau))$ where $W = CS_X + PS_X + CS_Y + PS_Y +TR$ is social welfare. Then do analysis...
					\end{itemize}
			\end{itemize}
		\item Comparison to GH94
			\begin{itemize}
				\item Contingent payments are hard to reconcile with uncertainty
				\item It's the truthful contribution schedule in GH94 that implies the constant weighting of $1+a$ for sectors represented by a lobby. Won't get this clean, constant weighting with other schedules.
				\item Gov't doesn't care about \textit{anything} because it gets the same payoff no matter what
					\begin{itemize}
						\item With one lobby, this lobby-has-all-the-bargaining-power feature is an equilibrium implication of the menu-auction set-up where the lobby makes a TIOLI offer
						\item Gov't gets all the surplus when there are two or more lobbies
						\item This result holds in DGH97, p. 767. Footnote 10 explicitly says that this is because lobby makes TIOLI offer.
						\item So go to MRC07 where bargaining power can be manipulated
					\end{itemize}
				\item Menu auction eqm requirement: $(C(\tau),\tau)$ must maximize joint surplus
					\begin{itemize}
						\item NB: $\tau$ that maximizes gov't welfare doesn't generically maximize joint surplus (unless it also maximizes lobby payoff)
						\item In my model, optimum for lobby would be prohibitive tariff, $e=0$. Joint optimum determined by $\frac{\partial \ga}{\partial e}\pi_X = 2$ and $\frac{\partial CS_X}{\partial \tau} + \left[ 1 + \ga(e)\right]\frac{\partial \pi_X}{\partial \tau} + \frac{\partial TR}{\partial \tau} = 0$. Not clear how this is related to lobby's problem, but likely to have higher $\tau$ and lower $e$ than government's optimum (unless $\ga$ changes very steeply between the two points $e_J$ and $e_G$)
						\item Careful of transferable vs. non-transferable utility
					\end{itemize}
				\item Not sure if contingent vs. non-contingent payments are a big deal
				\item If I change nothing else but subtract $C$ from gov't welfare function, no qualitative change b/c of 0 bargaining weight
			\end{itemize}
		\item MRC07
			\begin{itemize}
				\item Need case of fixed capital ($z=0$)
				\item NB (p. 1391): optimal trade agreement if lobbies have all the bargaining power and no ex-ante lobbying is free trade
					\begin{itemize}
						\item Page 26-28 of working paper has government with all the bargaining power (and no capital mobility, but remember that the capital owners choose where to invest in the first period). Here, could be free trade but could be interior to get some rents.
					\end{itemize}
				\item Then re-do MRC07 with $W(\tau) + g(e)$, and version where I subtract $e$
					\begin{itemize}
						\item Should have gov't make lobby indifferent and maximize joint surplus. But again, this doesn't necessarily maximize gov't welfare
						\item Or rather, should I follow Limao and Tovar?
					\end{itemize}
			\end{itemize}
	\end{itemize}

@@

\section{Lit review}
\begin{itemize}
	\item Find MRC cites (maybe some in Ethier) for why PE shocks can't be addressed
		\begin{itemize}
			\item Bagwell and Staiger 1999 AER
		\end{itemize}
	\item Have to make connection to endogenous papers clearer
		\begin{itemize}
			\item and make clear that GH is isomorphic / provides microfoundations for Baldwin objective function
			\item More on Coates $\&$ Ludema (2001)
		\end{itemize}
	\item I think that I need to bring people along more carefully from GH/MRC to what I'm doing
	\item Paola: How do I want to sell the paper?
		\begin{itemize}
			\item In relation to what literature?
				\begin{itemize}
					\item What literature does endogenous? Coates-Ludema 2001, MRC, GH
					\item What literature \textit{doesn't}?
				\end{itemize}
			\end{itemize}
	\item Review Bown, Bagwell $\&$ Staiger
	\item Do I include papers like BS2001 (non-repeated) in lit review?
	\item Read Rosendorff $\&$ Milner (2001) [from Cristiane Carneiro at PEIO]
	\item Kyle: McLaren in his chapter calls the Grossman and Helpman setup with
	 contributions `felonious'
	\item David DeRemer: Safeguards have dropped off in use around the world
		\begin{itemize}
			\item Look at U.S. vs. ROW (he sent papers)
		\end{itemize}
	\item Limao and Tovar 2011
		\begin{enumerate}
			\item Their 2nd (and final) stage is Nash bargaining. Is there an isomorphism to my setup?
			\item It IS clear to take their first, limited case of commitment to tariff cap only (ignore NTB) as analogy for gov't in my model choosing commitment to different tariff level. Need to answer Q1 above in order to answer points 3 and 4:
			\item Their gains from commitment derive from improvement in bargaining power vis-a-vis the lobby (Schelling conjecture invoked). How does this relate to the gain from commitment in my model?
			\item Top of page 6: ``large enough bargaining power.'' Can I make connection to $\ga(e)$?
			\item Note: in their equation 3, $C$ enters expression for NBS's ($\tau$) in equilibrium, it doesn't disappear as in GH
		\end{enumerate}
\end{itemize}

@@

\section{Motivation}
		\begin{itemize}
			\item What it's missing: Well articulated question / paradox (I think it's just not well-articulated)
			\item Intro doesn't reflect body of paper
			\item What kinds of empirical questions might we ask with this model?
			\item What would be different because we use this model?
			\item Starting from the introduction, I think you make a convincing case that it is important to endogenize the extent of political pressure and I believe this would be THE selling point of the paper. However, you have not completely sold your contribution and its novelty that you bring in the issue of the objective function of the government. Is this aspect crucial for the point you want to make? If yes, it should be integrate with the previous object from the beginning. If not, it should be postponed a bit.
			\item I also find the introduction too long. You could/should split the literature review that begins on page 4 to a separate section. And in any case, I found that you don't engage with the literature in terms of how you contribute/differentiate from it. Again, your main point seems to get lost into the discussion instead of standing out.
			\item You need to think a bit more about the objective(s) of the paper and how best to achieve them.
			\item Intro: GH gives micro foundations. But there are real consequences of endogenous politics.
		\end{itemize}
